Displacement of fishing effort by Large Scale Marine Protected Areas[^*]

### 2019-01-24 docs/PIPA_Palau.tex
Updated manuscript

\documentclass[11pt,english]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{chicago}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\author{
  Juan CarlosVillase\~{n}or-Derbez\footnote{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA} \\
  \texttt{juancarlos@ucsb.edu}
  \and
 John Lynham\footnote{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
  \texttt{lynham@hawaii.edu }
}

\date{Updated on: \today}

\usepackage{float}
\floatplacement{figure}{H}
\usepackage{lineno}
\linenumbers
\usepackage[bottom]{footmisc}
\usepackage{pdflscape}
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

% John's additional packages below

\usepackage{graphicx}
\graphicspath{{figures/}} %Setting the graphicspath

\begin{document}
\maketitle
\begin{abstract}
Large-scale Marine Protected Areas (LSMPAs) have seen a significant
increase over the last years. Fishing effort is effectively eliminated
within these protected areas upon implementation. The benefits of
reducing effort have been largely studied, but little empirical works
evaluate how vessels react and redistribute after an MPA is created. The
economic and ecological implications of displacing fishing effort are
not yet fully understood. We use identification of fishing activity via
Automatic Identification Systems (AIS) and causal inference techniques
to provide the first analysis of behavioral changes and spatial
redistribution of tuna purse seiners due to the implementation of a
Large Scale Marine Protected Area in the Pacific Ocean. Our work
provides three main findings: 1) aggregate fishing effort remains
relatively unaffected; 2) vessels that fished inside the protected area
redistribute to adjacent waters; and 3) we observe a crowding effect for
the first months after implementation. Our results not only provide an
impact evaluation of the effect of LSMPAs on fishing activity, but
provide insights into vessel redistribution dynamics, which may have
ecological and economic implications for marine conservation and fisheries
management. As countries continue to implement LSMPAs as a way to
reach the stated 10\% target of ocean protection, managers should
consider how fishing effort will change in space and through time to
ensure that fishing effort is not just displaced elsewhere, leading to
overfishing in adjacent waters. While LSMPAs can provide a wide
range of benefits, their implementation must be accompained with
traditional fisheries management to maximize their effectiveness.

@@

@@

\section{Introduction}\label{introduction}

Marine Protected Areas (MPAs) are intended to safeguard parts of the
ocean from fishing and other extractive activities. Current
international goals aim to protect 10\% of the ocean environment by
2020. In an effort to meet this target, there has been a rapid
increase recently in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
a small number of Large Scale Marine Protected Areas (LSMPAs).\footnote{See, for example, \citet{game_2009},  \citet{singleton_2014},\citet{boonzaier_2016}, \citet{mccauley_2016}, and \citet{alger_2017}.}
). Today, a small number of LSMPAs make up at least 80\%
of the managed areas in the ocean \citep{toonen_2013}.

@@

The empirical research that has been done in smaller sized MPAs
suggests that resource users may show idiosyncratic responses. For
example, \citet{stevenson_2013} show that a network of MPAs displaced
fishing effort farther away from ports, resulting in higher
\emph{perceived} costs, and increases in catch per unit effort.
\citet{cabral_2017} analyze the redistribution of fishing and
non-fishing vessels following the implementation of a network of MPAs in
California, and find that commercial dive boats (??????) follow a
fishing-the-line pattern, while some fishing boats follow an ideal free
distribution. More recently \citet{elahi_2018} used satellite tracking
data to show that a temporal spatial closure caused trawlers to maintain
effort but apply it more intensively elsewhere, particularly along the
borders and closer to shore. The way in which fishers react to a spatial
closure can have major implications for its outcome
\citep{smith_2003,hilborn_2006}, highlighting the need to understand how
fishers react to the implementation of LSMPAs, how fishing effort
changes, and how it is spatially redistributed. All these closures took
place within Exclusive Economic Zones, where other regulations exist.
This may not always be the case for LSMPAs, where often the entire EEZ
is converted into a LSMPA, leaving fishers with the option of moving to
the high seas or other countries' EEZs.

@@

\[
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t},
\]

@@

We discretize spatial units by creating a polygon for
PIPA and distinct
spatial units for each geographically separate EEZ of each country. Some vessels might shift
from EEZs into the high seas, but we are interested in knowing
\emph{where} in the high seas, so we incorporate additional regions by
using a 1 degree buffer of the high seas around each of the EEZ regions.
The rest of the high seas are merged into a single spatial unit. For
example, if we were to do this only for Kiribati, we would have 8
spatial units: PIPA, three EEZ units, three 1-degree buffers of high seas
around each EEZ, and the rest of the high seas. Whenever the buffer units
overlap, we randomly clip one on to the other (QUESTION FOR JC: WHAT DOES THIS MEAN?).

@@

\[
y_{i,t} = \alpha + \beta_1Year_t + \beta_{2,i}Region_i + \beta_{3,i}Year_t \times Region_i+ \epsilon_{i,t}
\]

Our variable of interest, \(y_{i,t}\) represents the proportion of
fishing hours that region \(i\) receives at time \(t\). Years are
modeled as factors (\(Year_t\)), using 2012 as the reference level.
\(Region\) is a dummy variable for regions defined above. Our parameter (QUESTION FOR JC: VECTOR?)
of interest is \(\beta_{3,i}\), which captures the yearly by-country
change in proportional allocation of fishing effort relative to 2012.

@@

We use the rasterized effort to evaluate if the PIPA closure increased
crowding outside the LSMPA. We count the number of raster cells that
had both treated and control vessels each year (Fig.
\ref{fig:sp_corr}A). The pattern observed here could just be an artifact
of satellite detections increasing though time. Therefore we also
calculate a spatial correlation of presence/absence and observe similar
patterns (Fig. \ref{fig:sp_corr}B). While this is at the year level and
cannot assure that vessels were in effect at the same time in the same
place, it provides a of what we would expect to
find if our claims of displacement are true. Spatial overlap increases
in 2015 as vessels from PIPA are excluded, but then starts to decline. [QUESTIONS FOR JC: Is this significant? Can we do a daily measure? What about mean or shortest distance between vessels. Treated/Control/Combined]

@@

@@

%\begin{figure}[h]
%	\caption{Map of the Four Protected Areas}
%	\label{fig:maps}
%	\includegraphics[width=0.8\textwidth]{Color_V1.png}
%	Notes: ... .
%\end{figure}

@@

\begin{figure}[h]
	\caption{Fishing Effort in Palau Relative to the Total PNA Area}
%	\includegraphics[width=0.75\textwidth]{Fishing_effort_Palau_relative_PNA}
\end{figure}

\begin{figure}[h]
	\caption{Fishing Effort in Palau Relative to the Total PNA Area By Distant Water Fishing Fleet}
%	\includegraphics[width=0.75\textwidth]{By_flag_Fishing_effort_Palau_relative_PNA}
\end{figure}

@@

\hypertarget{further-work}{%
\section{Further work}\label{further-work}}

\begin{itemize}
\tightlist
\item
  Distance traveled
\item
  Non-fishing hours at sea
\item
  Monthly crowdnes (same approach as now, but monthly instead of yearly)
\item
  Number of vessels per cell as another measure of crowdness (this is a
  more real one)
\item
  Repeat raster exercise for Revillagigedo and other recently
  implemented LSMPAs. It would be great to have a pannel figure of 3 or
  4 other LSMPAs that show wher effort was and where it went to
  generalize our results.
\item
  John talked about this being relevant to Palau (their upcoming LSMPA).
  We might want to talk about where the vessels that are there would go.
\end{itemize}

\bibliography{references}

>>>>

\documentclass[9pttwoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

@@

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{Juan CarlosVillase\~{n}or-Derbez}
\author[b,1]{John Lynham}

\affil[a]{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA}
\affil[b]{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}

% Please give the surname of the lead author for the running footer
\leadauthor{Villase\~{n}or-Derbez}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{All authors contributed equally to this work}
\authordeclaration{The authors declare that they have no conflicts of interest}
\equalauthors{\textsuperscript{1}J.C.V.D. and J.L. contributed equally to this work.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: juancarlos\@ucsb.edu}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Marine Protected Areas $|$ Fisheries $|$ Purse Seining $|$ Marine Conservation}

\begin{abstract}
Large-scale Marine Protected Areas (LSMPAs) have seen a significant
increase over the last years. Fishing effort is effectively eliminated
within these protected areas upon implementation. The benefits of
reducing effort have been largely studied, but little empirical works
evaluate how vessels react and redistribute after an MPA is created. The
economic and ecological implications of displacing fishing effort are
not yet fully understood. We use identification of fishing activity via
Automatic Identification Systems (AIS) and causal inference techniques
to provide the first analysis of behavioral changes and spatial
redistribution of tuna purse seiners due to the implementation of a
Large Scale Marine Protected Area in the Pacific Ocean. Our work
provides three main findings: 1) aggregate fishing effort remains
relatively unaffected; 2) vessels that fished inside the protected area
redistribute to adjacent waters; and 3) we observe a crowding effect for
the first months after implementation. Our results not only provide an
impact evaluation of the effect of LSMPAs on fishing activity, but
provide insights into vessel redistribution dynamics, which may have
ecological and economic implications for marine conservation and fisheries
management. As countries continue to implement LSMPAs as a way to
reach the stated 10\% target of ocean protection, managers should
consider how fishing effort will change in space and through time to
ensure that fishing effort is not just displaced elsewhere, leading to
overfishing in adjacent waters. While LSMPAs can provide a wide
range of benefits, their implementation must be accompained with
traditional fisheries management to maximize their effectiveness.

@@

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\usepackage{pdflscape}
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}\label{introduction}
\dropcap{M}arine Protected Areas (MPAs) are intended to safeguard parts of the
ocean from fishing and other extractive activities. Current
international goals aim to protect 10\% of the ocean environment by
2020. In an effort to meet this target, there has been a rapid
increase recently in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
a small number of Large Scale Marine Protected Areas (LSMPAs)\footnote{See, for example, \citep{game_2009,singleton_2014,boonzaier_2016,mccauley_2016,alger_2017}.}.
Today, a small number of LSMPAs make up at least 80\%
of the managed areas in the ocean \citep{toonen_2013}.

@@

The empirical research that has been done in smaller sized MPAs
suggests that resource users may show idiosyncratic responses. For
example, \citet{stevenson_2013} show that a network of MPAs displaced
fishing effort farther away from ports, resulting in higher
\emph{perceived} costs, and increases in catch per unit effort.
\citet{cabral_2017} analyze the redistribution of fishing and
non-fishing vessels following the implementation of a network of MPAs in
California, and find that dive boats follow a
fishing-the-line pattern, while some fishing boats follow an ideal free
distribution. More recently \citet{elahi_2018} used satellite tracking
data to show that a temporal spatial closure caused trawlers to maintain
effort but apply it more intensively elsewhere, particularly along the
borders and closer to shore. The way in which fishers react to a spatial
closure can have major implications for its outcome
\citep{smith_2003,hilborn_2006}, highlighting the need to understand how
fishers react to the implementation of LSMPAs, how fishing effort
changes, and how it is spatially redistributed. All these closures took
place within Exclusive Economic Zones, where other regulations exist.
This may not always be the case for LSMPAs, where often the entire EEZ
is converted into a LSMPA, leaving fishers with the option of moving to
the high seas or other countries' EEZs.

@@

\begin{figure*}[h]
\begin{align*}
log(y)_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t}
\label{eqn:did}
\end{align*}
\end{figure*}

@@

We discretize spatial units by creating a polygon for
PIPA and distinct
spatial units for each geographically separate EEZ of each country. Some vessels might shift
from EEZs into the high seas, but we are interested in knowing
\emph{where} in the high seas, so we incorporate additional regions by
using a 1 degree buffer of the high seas around each of the EEZ regions.
The rest of the high seas are merged into a single spatial unit. For
example, if we were to do this only for Kiribati, we would have 8
spatial units: PIPA, three EEZ units, three 1-degree\footnote{Currently running the 5-degree version too} buffers of high seas
around each EEZ, and the rest of the high seas. We clipped any overlapping
high seas buffers to avoid duplication.

@@

\begin{figure*}[h]
\begin{align*}
y_{i,t} = \alpha + \beta_1Year_t + \beta_{2,i}Region_i + \beta_{3,i}Year_t \times Region_i+ \epsilon_{i,t}
\end{align*}
\end{figure*}

Our variable of interest, $y_{i,t}$ represents the proportion of
fishing hours that region $i$ receives at time $t$. Years are
modeled as factors ($Year_t$), using 2012 as the reference level.
\(Region\) is a dummy variable for regions defined above. Our vector of parameters of
of interest is $\beta_{3,i}$, which captures the yearly by-country
change in proportional allocation of fishing effort relative to 2012.

Finally, we inspect the crowding effects that may arise due to the reduction
in total fishing area. We use the rasterized fishing effort and calculate two
potential indices of crowding. For the first one, we count the number of cells
that had fishing activity from both groups over a given month. For the second one,
we calculate the correlation of presence/absence of fishing for both groups
over one month. If the implementation of the reserve induces a crowding effect,
we would expect to observe bo clear trend before the implementation of the reserve.
The implementation would be followed by an increase in these measures, which, 
if vessels avoid crowding, should then come back down. We therefore expect to
have three inflection points: 1) when there is an initial increase due to MPA
implementation, 2) When the crowding has reached its maximum and then decreases,
and 3) when the decrease in the measure levels off, pressumably to pre-MPA levels.
For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by
centering our time series of crowding indices on the day of implementation. Our
explanatory variable is then the number of months before or after the implementation.
For example, since PIPA was implemented in January 1st of 2015, December of 2014 
has a value of -1, whicle Feb of 2015 would receive a value of 1.

\begin{figure*}[h]
\begin{align*}
y_t = \alpha + \beta_1 month_t + \beta_2 month_t^2 + \beta_3 month_t^3 + \beta_4 month_t ^4 + \epsilon_t
\end{align*}
\end{figure*}

@@

We use the rasterized effort to evaluate if the PIPA closure increased
crowding outside the LSMPA. We count the number of raster cells that
had both treated and control vessels each month (Fig.
\ref{fig:sp_corr}A). The pattern observed here could just be an artifact
of satellite detections increasing though time. Therefore we also
calculate a spatial correlation of presence/absence and observe similar
patterns (Fig. \ref{fig:sp_corr}B). Spatial overlap increases
in 2015 as vessels from PIPA are excluded, but then starts to decline.

@@

\begin{figure}
\centering
\includegraphics{img/VDS_year.pdf}
\caption{\label{fig:VDS_year}Vessel-days for all PNA countries (including Tokelau).}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/VDS_country_year.pdf}
\caption{\label{fig:VDS_country_year}Vessel-days for all PNA countries (including Tokelau) by country.
The top panel shows vessel days in absolute numbers, while the bottom panel shows the proportion
of each year. The left and right columns show fishing and non-fishing hours.
[JOHN: I prefer the absolute hours one, but what do you prefer?]}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/hist_kir_fishing.pdf}
\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place
within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel
}
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
	\caption{Map of the Four Protected Areas}
	\label{fig:maps}
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=0.75\textwidth]{img/Fishing_effort_Palau_relative_PNA}
	\caption{Fishing Effort in Palau Relative to the Total PNA Area}
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.75\textwidth]{img/By_flag_Fishing_effort_Palau_relative_PNA}
	\caption{Fishing Effort in Palau Relative to the Total PNA Area By Distant Water Fishing Fleet}
\end{figure}

@@

\section{References}\label{references}
\bibliography{references}

### 2019-01-24 docs/tab/sp_corr.tex
Updated manuscript

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Constant & 76.695$^{***}$ (4.382) & 76.695$^{***}$ (4.382) \\ 
  Months & 4.342$^{***}$ (0.419) & 4.342$^{***}$ (0.419) \\ 
  Months $^2$ & $-$0.026$^{***}$ (0.007) & $-$0.026$^{***}$ (0.007) \\ 
  Months $^3$ & $-$0.003$^{***}$ (0.0004) & $-$0.003$^{***}$ (0.0004) \\ 
 \hline \\[-1.8ex] 
Month FE & Yes & Yes \\ 
Flag FE & Yes & Yes \\ 
Observations & 72 & 72 \\ 
R$^{2}$ & 0.704 & 0.704 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Constant & 65.538$^{***}$ (5.878) & 0.409$^{***}$ (0.016) \\ 
  Months & 4.429$^{***}$ (0.402) & 0.010$^{***}$ (0.001) \\ 
  Months $^2$ & 0.060$^{*}$ (0.033) & 0.00003 (0.0001) \\ 
  Months $^3$ & $-$0.004$^{***}$ (0.0004) & $-$0.00001$^{***}$ (0.00000) \\ 
  I(dif$\hat{\mkern6mu}$4) & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
 \hline \\[-1.8ex] 
Month FE & Yes & Yes \\ 
Flag FE & Yes & Yes \\ 
Observations & 72 & 72 \\ 
R$^{2}$ & 0.741 & 0.631 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-01-24 rmd/Manuscript.Rmd
Updated manuscript

<!-- antes de 06/01/14 habian 3 sats, despues 6 hasta 12/31/15, luego 10 hasta 2017 y ahora hay muchos jaja -->

@@

```{r, eval = F}
# Map with color of each shapefile representing the change for 2015
change_2015_by_region <- commarobust::commarobust_tidy(model) %>%
  filter(str_detect(term, ":")) %>%
  mutate(year = as.numeric(str_extract(term, "[:digit:]+")),
         term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05"),
         term = str_replace(term, "id", ""),
         term = fct_relevel(term, terms_order)) %>% 
  filter(year == 2015) %>%
  rename(id = term)

@@

regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
                   layer = "regions") %>% 
  filter(!id %in% eezs_exclude) %>%
  left_join(change_2015_by_region, by = "id")

ggplot() +
  geom_sf(data = regions, aes(fill = est)) +
  scale_fill_gradientn(colours = colorRamps::matlab.like(20)) +
  ggtheme_plot() +
  guides(fill = guide_colorbar(title = bquote(Delta)))

>>>>

@@

```{r, eval = F}
# Map with color of each shapefile representing the change for 2015
change_2015_by_region <- commarobust::commarobust_tidy(model) %>%
  filter(str_detect(term, ":")) %>%
  mutate(year = as.numeric(str_extract(term, "[:digit:]+")),
         term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05"),
         term = str_replace(term, "id", ""),
         term = fct_relevel(term, terms_order2)) %>% 
  filter(year == 2015) %>%
  rename(id = term)

@@

regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
                   layer = "regions") %>% 
  # filter(!id %in% eezs_exclude) %>%
  left_join(change_2015_by_region, by = "id")

ggplot() +
  geom_sf(data = regions, aes(fill = est)) +
  scale_fill_gradientn(colours = colorRamps::matlab.like(20)) +
  # ggtheme_plot() +
  guides(fill = guide_colorbar(title = bquote(Delta)))
